---
title: DANL Project
subtitle: "Slam Dunk Salaries: Analyzing NBA PLayer Earnings"
author: 
  - Luca Schettino
  - Owen Ellick
  - Jack Helrigel
  - Jake Starkey

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project :clap:
Welcome to our project, where we dive into the dynamic world of professional basketball through the lens of salaries and performance statistics. We will analyize a dataset with NBA player Salaries and statistics from the 2022-2023 NBA season.

```{r}
library(tidyverse)
library(skimr)
```


# Data

The data.frame `NBAsal` contains data from the 2022-2023 NBA season. It contains player per-game and advanced statistics for that season with player salary data. This allows us to create a comprehensive resource for understanding the performance and financial aspects of professional basketball players.


## Summary Statistics

```{r}
nba_salaries <- read_csv("nba_salaries.csv")
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(nba_salaries) 
```


```{r}
skim(nba_salaries) %>% 
  select(-n_missing)
```


## Top Players and Points Per Game

The following shows the top 10 players during the NBA 2022-2023 season based on the number of points per game.

```{r}
top_10_players <- nba_salaries %>% 
  group_by(PTS) %>% 
  arrange(desc(PTS)) %>% 
  head(10) %>% 
  relocate(PTS,.before = Position)

top_10_players
```

Comments:

- Joel Embiid, Damian Lillard, Shai Gilgeous-Alexander, Giannis Antetokounmpo, Jayson Tatum, Stephen Curry, Kevin Durrant, Lebron James, Donovan Mitchell, and Devin Booker are the top 10 players based on points per game for the 2022-2023 NBA Season.
